Tables/Graphs for Article

### 2018-03-06 article/graphics.Rmd
updated how data is read in
added code to extract SE of model coefficients

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
list <- oshitar::variable_setup(out)
x <- list[[1]]

@@

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                    contain_unanswered + contain_answered + title_questionmark + 
                    text_contain_punct + text_all_lower + update + prior_effort + 
                    day + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + 
                    rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + 
                    rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
model
```

>>>>

```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
x <- oshitar::variable_setup(out)

@@

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                    contain_unanswered + contain_answered + title_questionmark + 
                    text_contain_punct + text_all_lower + update + prior_effort + 
                    day + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + 
                    rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + 
                    rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)

model_coefs <- data.frame(vars = names(model$coefficients), 
                          beta = unname(model$coefficients)) %>% mutate(HR = exp(beta))
model_var <- as.data.frame(model$var)

model_coefs$SE <- 0
for (i in 1:32) {
  model_coefs$SE[i] <- sqrt(model_var[i, i])
}

model_coefs$upper <- exp(model_coefs$beta + (1.96 * model_coefs$SE))
model_coefs$lower <- exp(model_coefs$beta - (1.96 * model_coefs$SE))
```
